---
title: "Structure Summary Outputs"
author: "Sam Graf"
date: "3/23/2021"
output: pdf_document
---
# LV data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(here)

RA <- read.csv(here("UAR_RapidAssessmentforStructures_RInput_2020_ER_SG.csv"))

LV <- read.csv("LogVaneAnalysis_RInput_2020_ver4.csv")
LV$Integrity <- as.numeric(LV$Integrity)
LV$Deposition <- as.numeric(LV$Deposition)
LV$Erosion <- as.numeric(LV$Erosion)

#removes 3 strctures by this method
max_scores <- LV %>%
  
  filter(Integrity != "Removed") %>%
  group_by(Num, LV_Angle, LV_Slope,Associated_Residual_Pool,Morphology_Pre) %>%
  summarise(max_int_score = max(Integrity))

max_scores %>%
  group_by(max_int_score) %>%
  count(max_int_score)


```

```{r  first year impairemnet functions, include = FALSE}
#for erosion, deposition and rootwads, the scores go up to 5
find_first_year_of_impairment_integrity <- function (RA_data) {
  RA_data$fir_imp_yr_integrity <- 0 ##needs to be outside the for loop
  for (str_num in unique(RA_data$Num)) {
    #print(str_num)
    #finds how many rows the structure was iagnosed with 3 or 4
    impaired_rows <- which((RA_data$Integrity == 3 | RA_data$Integrity == 4) & RA_data$Num == str_num) #makes vector of which rows a specific structure was impaired or failed
    #print(length(impaired_rows))
    
    #if the length of that vector is 0 then it 
    if (length(impaired_rows > 0)) {
      #print(c("This structure was impaired or failed"))
      minval <- min(impaired_rows)
      #print(minval)
      RA_data[minval, c("fir_imp_yr_integrity")] <- 1
      print(paste("first impaired year: ", RA_data$Year[minval], "entered for", str_num, "in row ", minval))
      
      
    }
    else {
      print(paste(str_num, "structure wasnt impaired ever"))
      # RA_data[minval, c("fir_imp_yr")] <- 0
    }
    
  }
  return (RA_data)
}

find_first_year_of_impairment_erosion <- function (RA_data) {
  RA_data$fir_imp_yr_erosion <- 0 ##needs to be outside the for loop
  for (str_num in unique(RA_data$Num)) {
    #print(str_num)
    #finds how many rows the structure was iagnosed with 3 or 4
    impaired_rows <- which((RA_data$Erosion == 3 | RA_data$Erosion == 4 | RA_data$Erosion == 5) & RA_data$Num == str_num) #makes vector of which rows a specific structure was impaired or failed
    #print(length(impaired_rows))
    
    #if the length of that vector is 0 then it 
    if (length(impaired_rows > 0)) {
      #print(c("This structure was impaired or failed"))
      minval <- min(impaired_rows)
      #print(minval)
      RA_data[minval, c("fir_imp_yr_erosion")] <- 1
      print(paste("first impaired erosion year: ", RA_data$Year[minval], "entered for structure ", str_num, "in row ", minval))
      
      
    }
    else {
      print(paste(str_num, "structure wasnt impaired by erosion ever"))
      # RA_data[minval, c("fir_imp_yr")] <- 0
    }
    
  }
  return (RA_data)
}

find_first_year_of_impairment_deposition <- function (RA_data) {
  RA_data$fir_imp_yr_deposition <- 0 ##needs to be outside the for loop
  for (str_num in unique(RA_data$Num)) {
    #print(str_num)
    #finds how many rows the structure was iagnosed with 3 or 4
    impaired_rows <- which((RA_data$Deposition == 3 | RA_data$Deposition == 4| RA_data$Deposition == 5) & RA_data$Num == str_num) #makes vector of which rows a specific structure was impaired or failed
    #print(length(impaired_rows))
    
    #if the length of that vector is 0 then it 
    if (length(impaired_rows > 0)) {
      #print(c("This structure was impaired or failed"))
      minval <- min(impaired_rows)
      #print(minval)
      RA_data[minval, c("fir_imp_yr_deposition")] <- 1
      print(paste("first impaired Deposition year: ", RA_data$Year[minval], "entered for", str_num, "in row ", minval))
      
      
    }
    else {
      print(paste(str_num, "structure wasnt impaired Deposition ever"))
      # RA_data[minval, c("fir_imp_yr")] <- 0
    }
    
  }
  return (RA_data)
}

find_first_year_of_impairment_Rootwad <- function (RA_data) {
  RA_data$fir_imp_yr_rootwad <- 0 ##needs to be outside the for loop
  for (str_num in unique(RA_data$Num)) {
    #print(str_num)
    #finds how many rows the structure was iagnosed with 3 or 4
    impaired_rows <- which((RA_data$Rootwad_Performance == 3 | RA_data$Rootwad_Performance == 4 | RA_data$Rootwad_Performance == 5) & RA_data$Num == str_num) #makes vector of which rows a specific structure was impaired or failed
    #print(length(impaired_rows))
    
    #if the length of that vector is 0 then it 
    if (length(impaired_rows > 0)) {
      #print(c("This structure was impaired or failed"))
      minval <- min(impaired_rows)
      #print(minval)
      RA_data[minval, c("fir_imp_yr_rootwad")] <- 1
      print(paste("first impaired Rootwad year: ", RA_data$Year[minval], "entered for", str_num, "in row ", minval))
      
      
    }
    else {
      print(paste(str_num, "structure wasnt impaired Rootwad ever"))
      # RA_data[minval, c("fir_imp_yr")] <- 0
    }
    
  }
  return (RA_data)
}



```

Number of log vanes scoring 3 or higher based on Pre existing Morphology
```{r, echo = FALSE}
x <- max_scores %>%
  mutate(failed = case_when(
    max_int_score == 3 | max_int_score == 4 ~ TRUE,
    max_int_score == 1 | max_int_score == 2 ~ FALSE
  )) %>%
  group_by(Morphology_Pre, failed) %>%
  summarize(percent = 100* (n()/length(unique(max_scores$Num))))
kable(x, caption = "Log Vanes Scoring >= 3 by Pre Existing Morphology")
```

Number of Log Vanes scoring 3 or higher based on pre existing morphology by Year; denominator is total number of LV (41)
18 LV were diagnosed 3 or 4 at some point during monitoring.

```{r, include = FALSE}
LV <- find_first_year_of_impairment_integrity(LV)

y1 <- LV %>%
  group_by(Year, Morphology_Pre) %>%
  summarise(new_impaired = sum(fir_imp_yr_integrity), perc_new_impaired = round((100*(new_impaired/(length(unique(LV$Num))))),2))

```

```{r, echo = FALSE}

y1 %>%
  ggplot(aes(x = Year, y = perc_new_impaired)) +
  geom_bar(stat = "identity", position = "dodge", aes(fill = Morphology_Pre)) +
  theme_classic() +
  labs(title = "New Structure 3s and 4s by Year", y = "% Newly Impaired", x = "Year")

y1 <- y1 %>%
  select(-new_impaired) %>%
  pivot_wider(names_from = Year, values_from = perc_new_impaired)



kable(y1, caption = "Log Vane Failures by Year and Pre-existing Morphology")

```
# RA Data
## Intact Structures

```{r, include = FALSE}
y <- RA
rtwads <- y %>%
  filter(!is.na(Rootwad_Performance))
rtwads_structures <- length(unique(rtwads$Num))

###Structures still intact: integrity
still_intact_integrity <- y %>%
  filter(!is.na(Integrity)) %>%
  mutate(still_intact = case_when(
    Integrity == 1 | Integrity == 2 ~ 1,
    Integrity == 3 | Integrity == 4 ~ 0
  )) %>%
  count(Year, still_intact) 

x4 <- still_intact_integrity %>%
  group_by(Year) %>%
  summarize(total_structures = sum(n)) %>%
  ungroup()

still_intact_integrity2 <- left_join(still_intact_integrity, x4, by = "Year")
  

#mutate(Percent = round(100*(n / length(unique(RA$Num))),2))
#final [ivot wider table to later join]
still_intact_integrity3 <- still_intact_integrity2 %>%
  mutate(Percent = round(100*(n/total_structures),2)) %>%
  filter(still_intact == 1) %>%
  select(-n,-total_structures) %>%
  pivot_wider(names_from = Year,values_from = Percent)

###Depositon
still_intact_Deposition <- y %>%
  filter(!is.na(Deposition)) %>%
  mutate(still_intact = case_when(
    Deposition == 0 | Deposition == 1 | Deposition == 2 ~ 1,
    Deposition == 3 | Deposition == 4 | Deposition == 5 ~ 0
  )) %>%
  count(Year, still_intact) 

x4 <- still_intact_Deposition %>%
  group_by(Year) %>%
  summarize(total_structures = sum(n)) %>%
  ungroup()

still_intact_Deposition2 <- left_join(still_intact_Deposition, x4, by = "Year")


#final pivot wider table to later join
still_intact_Deposition3 <- still_intact_Deposition2 %>%
  mutate(Percent = round(100*(n/total_structures),2)) %>%
  filter(still_intact == 1) %>%
  select(-n,-total_structures) %>%
  pivot_wider(names_from = Year,values_from = Percent)

###Erosion
still_intact_Erosion <- y %>%
  filter(!is.na(Erosion)) %>%
  mutate(still_intact = case_when(
    Erosion == 0 | Erosion == 1 | Erosion == 2 ~ 1,
    Erosion == 3 | Erosion == 4 | Erosion == 5 ~ 0
  )) %>%
  count(Year, still_intact) 

x4 <- still_intact_Erosion %>%
  group_by(Year) %>%
  summarize(total_structures = sum(n)) %>%
  ungroup()

still_intact_Erosion2 <- left_join(still_intact_Erosion, x4, by = "Year")


#final pivot wider table to later join
still_intact_Erosion3 <- still_intact_Erosion2 %>%
  mutate(Percent = round(100*(n/total_structures),2)) %>%
  filter(still_intact == 1) %>%
  select(-n,-total_structures) %>%
  pivot_wider(names_from = Year,values_from = Percent)

###Rootwad
still_intact_rootwad <- y %>%
  filter(!is.na(Rootwad_Performance)) %>%
  mutate(still_intact = case_when(
    Rootwad_Performance == 0 | Rootwad_Performance == 1 | Rootwad_Performance == 2 ~ 1,
    Rootwad_Performance == 3 | Rootwad_Performance == 4 | Rootwad_Performance == 5 ~ 0
  )) %>%
  count(Year, still_intact) 

#don't need this part; theres 22 structures measured every year for wood toe
# x4 <- still_intact_rootwad %>%
#   group_by(Year) %>%
#   summarize(total_structures = sum(n)) %>%
#   ungroup()
# 
# still_intact_rootwad2 <- left_join(still_intact_rootwad, x4, by = "Year")


#final pivot wider table to later join
#case here where rootwad got a 4 then dropped back down; structure 75
still_intact_rootwad3 <- still_intact_rootwad %>%
  mutate(Percent = round(100*(n/rtwads_structures),2)) %>%
  filter(still_intact == 1) %>%
  select(-n) %>%
  pivot_wider(names_from = Year,values_from = Percent)


#binding rows
x <- bind_rows(still_intact_integrity3, still_intact_Deposition3, still_intact_Erosion3, still_intact_rootwad3)
x$still_intact[1] <- "Integrity"
x$still_intact[2] <- "Deposition"
x$still_intact[3] <- "Erosion"
x$still_intact[4] <- "Rootwad"
names(x)[1] <- "Rating"


```
Intact Structures by Year
```{r, echo = FALSE}
kable(x, caption = "Percent Intact by Year for Rating Types")
```

### Intact Structures by Structure Type
```{r, include = FALSE}
## intact

still_intact_integrity_structures <- y %>%
  filter(!is.na(Integrity)) %>%
  mutate(still_intact = case_when(
    Integrity == 1 | Integrity == 2 ~ 1,
    Integrity == 3 | Integrity == 4 ~ 0
  )) %>%
  count(Year, still_intact, Structure_Type) 

x4 <- still_intact_integrity_structures %>%
  group_by(Year, Structure_Type) %>%
  summarize(total_structures = sum(n)) %>%
  ungroup()

still_intact_integrity_structures2 <- left_join(still_intact_integrity_structures, x4, by = c("Year", "Structure_Type"))


#mutate(Percent = round(100*(n / length(unique(RA$Num))),2))
#final [ivot wider table to later join]
still_intact_integrity_structures3 <- still_intact_integrity_structures2 %>%
  mutate(Percent = round(100*(n/total_structures),2)) %>%
  filter(still_intact == 1) %>%
  select(-n,-total_structures) %>%
  pivot_wider(names_from = Year,values_from = Percent)

##Deposition

still_intact_Deposition_structures <- y %>%
  filter(!is.na(Deposition)) %>%
  mutate(still_intact = case_when(
    Deposition == 0 | Deposition == 1 | Deposition == 2 ~ 1,
    Deposition == 3 | Deposition == 4 | Deposition == 5 ~ 0
  )) %>%
  count(Year, still_intact, Structure_Type) 

x4 <- still_intact_Deposition_structures %>%
  group_by(Year, Structure_Type) %>%
  summarize(total_structures = sum(n)) %>%
  ungroup()

still_intact_Deposition_structures2 <- left_join(still_intact_Deposition_structures, x4, by = c("Year", "Structure_Type"))


#mutate(Percent = round(100*(n / length(unique(RA$Num))),2))
#final [ivot wider table to later join]
still_intact_Deposition_structures3 <- still_intact_Deposition_structures2 %>%
  mutate(Percent = round(100*(n/total_structures),2)) %>%
  filter(still_intact == 1) %>%
  select(-n,-total_structures) %>%
  pivot_wider(names_from = Year,values_from = Percent)

##Erosion

still_intact_Erosion_structures <- y %>%
  filter(!is.na(Erosion)) %>%
  mutate(still_intact = case_when(
    Erosion == 0 | Erosion == 1 | Erosion == 2 ~ 1,
    Erosion == 3 | Erosion == 4 | Erosion == 5 ~ 0
  )) %>%
  count(Year, still_intact, Structure_Type) 

x4 <- still_intact_Erosion_structures %>%
  group_by(Year, Structure_Type) %>%
  summarize(total_structures = sum(n)) %>%
  ungroup()

still_intact_Erosion_structures2 <- left_join(still_intact_Erosion_structures, x4, by = c("Year", "Structure_Type"))


#mutate(Percent = round(100*(n / length(unique(RA$Num))),2))
#final [ivot wider table to later join]
still_intact_Erosion_structures3 <- still_intact_Erosion_structures2 %>%
  mutate(Percent = round(100*(n/total_structures),2)) %>%
  filter(still_intact == 1) %>%
  select(-n,-total_structures) %>%
  pivot_wider(names_from = Year,values_from = Percent)

#rootwad
still_intact_Rootwad_structures <- y %>%
  filter(!is.na(Rootwad_Performance)) %>%
  mutate(still_intact = case_when(
    Rootwad_Performance == 0 | Rootwad_Performance == 1 | Rootwad_Performance == 2 ~ 1,
    Rootwad_Performance == 3 | Rootwad_Performance == 4 | Rootwad_Performance == 5 ~ 0
  )) %>%
  count(Year, still_intact, Structure_Type) 

# x4 <- still_intact_Rootwad_structures %>%
#   group_by(Year, Structure_Type) %>%
#   summarize(total_structures = sum(n)) %>%
#   ungroup()
# 
# still_intact_Rootwad_structures2 <- left_join(still_intact_Rootwad_structures, x4, by = c("Year", "Structure_Type"))


#mutate(Percent = round(100*(n / length(unique(RA$Num))),2))
#final [ivot wider table to later join]
still_intact_Rootwad_structures3 <- still_intact_Rootwad_structures %>%
  mutate(Percent = round(100*(n/rtwads_structures),2)) %>%
  filter(still_intact == 1) %>%
  select(-n,) %>%
  pivot_wider(names_from = Year,values_from = Percent)

## Summary column


#INTEGIRTY SUMMARY COLUMN
# x <- RA %>%
#   mutate(failed = ifelse((Integrity >= 3), 1, 0))   # | is OR operator; Integrity == 3 | if we want to do "impaired" instead of failed

x <- RA

x <- find_first_year_of_impairment_integrity(x)
x1 <- x %>%
  group_by(Year, Structure_Type) %>%
  summarise(total_str_num = length(unique(Num)),
            total_impaired = sum(fir_imp_yr_integrity))
#checking to make sure we have 137 total structures
test1 <- x1 %>%
  ungroup() %>%
  select(-Year,-total_impaired) %>%
  distinct()
sum(test1$total_str_num)

# group_by(Structure_Type) %>%
# summarize(sum1 = sum(total_str_num))
integrity_structures_sum <- x1 %>%
  group_by(Structure_Type) %>%
  summarize(total_allyrs = sum(total_impaired),
            total_intact_structures = (total_str_num - total_allyrs),
            Percent_Intact = round(100*(total_intact_structures / total_str_num),2)) %>%
  distinct() %>%
  select(-total_allyrs, -total_intact_structures)

still_intact_integrity_structures4 <- left_join(still_intact_integrity_structures3, integrity_structures_sum, by = "Structure_Type")

still_intact_integrity_structures4 <- still_intact_integrity_structures4 %>%
  select(-still_intact)


#DEPOSITION SUMMARY COLUMN
x <- RA

x <- find_first_year_of_impairment_deposition(x)
x1 <- x %>%
  group_by(Year, Structure_Type) %>%
  summarise(total_str_num = length(unique(Num)),
            total_impaired = sum(fir_imp_yr_deposition))

deposition_structures_sum <- x1 %>%
  group_by(Structure_Type) %>%
  summarize(total_allyrs = sum(total_impaired),
            total_intact_structures = (total_str_num - total_allyrs),
            percentage = round(100*(total_intact_structures / total_str_num),2)) %>%
  distinct() %>%
  select(-total_allyrs, -total_intact_structures)

still_intact_Deposition_structures4 <- left_join(still_intact_Deposition_structures3, deposition_structures_sum, by = "Structure_Type")

still_intact_Deposition_structures4 <- still_intact_Deposition_structures4 %>%
  select(-still_intact)

#EROSION SUMMARY COLUMN
x <- RA

x <- find_first_year_of_impairment_erosion(x)
x1 <- x %>%
  group_by(Year, Structure_Type) %>%
  summarise(total_str_num = length(unique(Num)),
            total_impaired = sum(fir_imp_yr_erosion))

erosion_structures_sum <- x1 %>%
  group_by(Structure_Type) %>%
  summarize(total_allyrs = sum(total_impaired),
            total_intact_structures = (total_str_num - total_allyrs),
            percentage = round(100*(total_intact_structures / total_str_num),2)) %>%
  distinct() %>%
  select(-total_allyrs, -total_intact_structures)

still_intact_Erosion_structures4 <- left_join(still_intact_Erosion_structures3, erosion_structures_sum, by = "Structure_Type")

still_intact_Erosion_structures4 <- still_intact_Erosion_structures4 %>%
  select(-still_intact)

#ROOTWAD SUMMARY COLUMN
x <- find_first_year_of_impairment_Rootwad(x)
x1 <- x %>%
  group_by(Year, Structure_Type) %>%
  summarise(total_str_num = length(unique(Num)),
            total_impaired = sum(fir_imp_yr_rootwad))

rootwad_structures_sum <- x1 %>%
  group_by(Structure_Type) %>%
  summarize(total_allyrs = sum(total_impaired),
            total_intact_structures = (total_str_num - total_allyrs),
            percentage = round(100*(total_intact_structures / total_str_num),2)) %>%
  distinct() %>%
  select(-total_allyrs, -total_intact_structures)

still_intact_Rootwad_structures4 <- left_join(still_intact_Rootwad_structures3, rootwad_structures_sum, by = "Structure_Type")

still_intact_Rootwad_structures4 <- still_intact_Rootwad_structures4 %>%
  select(-still_intact)

```
Integrity
```{r, echo = FALSE}
kable(still_intact_integrity_structures4, caption = "Integrity of Structures by Year")
```
Deposition
```{r, echo = FALSE}
kable(still_intact_Deposition_structures4, caption = "Deposition of Structures by Year")
```
Erosion
```{r, echo = FALSE}
kable(still_intact_Erosion_structures4, caption = "Erosion of Structures by Year")
```
Rootwad
```{r, echo = FALSE}
kable(still_intact_Rootwad_structures4, caption = "Rootwad Performance of Structures by Year")
```



## Structure Failures
```{r, echo = FALSE, include = FALSE}
#RA <- read.csv(file.choose())
x <- RA %>%
  mutate(YAC = Year-2013, #gets number of years after 2013 the strucutre is
         failed = ifelse((Integrity == 4 | Integrity == 3), 1, 0))   # | is OR operator; Integrity == 3 | if we want to do "impaired" instead of failed

y <- find_first_year_of_impairment_integrity(x)
y <- find_first_year_of_impairment_deposition(y)
y <- find_first_year_of_impairment_erosion(y)
y <- find_first_year_of_impairment_Rootwad(y)

master1 <- y



###integrity: gives first years a structure was impaired (3 or 4)
integrity1 <- y %>%
  filter(`fir_imp_yr_integrity` == TRUE ) %>%
  group_by(Year) %>%
  count(fir_imp_yr_integrity == 1) %>%
  mutate(Percent = round(100 * (n / length(unique(y$Num))),2)) #adding this row will get a percentage of all structures


integrity2 <- integrity1 %>%
  select(-n) %>%
  pivot_wider(names_from = Year, values_from = Percent)

###Deposition
deposition1 <- y %>%
  filter(fir_imp_yr_deposition == TRUE ) %>%
  group_by(Year) %>%
  count(fir_imp_yr_deposition == 1) %>%
  mutate(Percent = round(100 * (n / length(unique(y$Num))),2)) #adding this row will get a percentage of all structures

deposition2 <- deposition1 %>%
  select(-n) %>%
  pivot_wider(names_from = Year, values_from = Percent)

###erosion
erosion1 <- y %>%
  filter(fir_imp_yr_erosion == TRUE ) %>%
  group_by(Year) %>%
  count(fir_imp_yr_erosion == 1) %>%
  mutate(Percent = round(100 * (n / length(unique(y$Num))),2)) #adding this row will get a percentage of all structures

erosion2 <- erosion1 %>%
  select(-n) %>%
  pivot_wider(names_from = Year, values_from = Percent)

###rootwad
rtwads <- y %>%
  filter(!is.na(Rootwad_Performance))
rtwads_structures <- length(unique(rtwads$Num))


rootwad1 <- y %>%
  filter(fir_imp_yr_rootwad == TRUE ) %>%
  group_by(Year) %>%
  count(fir_imp_yr_rootwad == 1) %>%
  mutate(Percent = round(100 * (n / rtwads_structures),2)) #adding this row will get a percentage of all structures



rootwad2 <- rootwad1 %>%
  select(-n) %>%
  pivot_wider(names_from = Year, values_from = Percent)

#binding rows
x <- bind_rows(integrity2, deposition2, erosion2, rootwad2)
x <- x %>%
  mutate(Ratings = case_when(`fir_imp_yr_integrity == 1`== TRUE ~ "Integrity",
                   `fir_imp_yr_deposition == 1`== TRUE ~ "Deposition",
                   `fir_imp_yr_erosion == 1`== TRUE ~ "Erosion",
                   `fir_imp_yr_rootwad == 1`== TRUE ~ "Rootwad"))

x1 <- x %>%
  select(Ratings, `2014`,`2015`, `2016`,`2017`,`2018`,`2020`)

x1[is.na(x1)] <- 0
x1 <- x1 %>%
  mutate(notes = "ratings >= 3")

```
Table that shows new scores of 3 or higher for each type of Rating in each Year.
Denominator is total structures Erosion, Integrity and Deposition (137). Denominator is total rootwad structures for rootwad (22).
After  structure is counted as "failed" for a year, it's not counted again
```{r, echo = FALSE}
kable(x1, caption = "New Failures for Rating Types")
```



## RA Failed Structures Summary of Ratings by Structure Types

Integrity: Denominator is structures of that same type. 
```{r, include= FALSE}
x <- RA
x <- find_first_year_of_impairment_integrity(x)
x1 <- x %>%
  group_by(Year, Structure_Type) %>%
  summarise(total_str_num = length(unique(Num)),
            total_impaired = sum(fir_imp_yr_integrity))

x2 <- x1 %>%
  mutate(Percent = round(100*(total_impaired/total_str_num),2))

x3 <- x2 %>%
  select(-total_str_num, -total_impaired) %>%
  pivot_wider(names_from = Year, values_from = Percent)
x3 <- x3 %>%
  mutate(Notes = "ratings >= 3")

```

```{r, echo = FALSE}

kable(x3, caption = "Integrity Diagnoses of 3 or 4", digits = 3)

```
Deposition

```{r, include = FALSE}
x <- RA
x <- find_first_year_of_impairment_deposition(x)
x1 <- x %>%
  group_by(Year, Structure_Type) %>%
  summarise(total_str_num = length(unique(Num)),
            total_impaired = sum(fir_imp_yr_deposition))

x2 <- x1 %>%
  mutate(Percent = round(100*(total_impaired/total_str_num),2))

x3 <- x2 %>%
  select(-total_str_num, -total_impaired) %>%
  pivot_wider(names_from = Year, values_from = Percent)
x3 <- x3 %>%
  mutate(Notes = "ratings >= 3")

```

```{r, echo = FALSE}

kable(x3, caption = "Deposition Diagnoses of 3 or 4 or 5", digits = 3)

```

Erosion
```{r, include = FALSE}
x <- RA
x <- find_first_year_of_impairment_erosion(x)
x1 <- x %>%
  group_by(Year, Structure_Type) %>%
  summarise(total_str_num = length(unique(Num)),
            total_impaired = sum(fir_imp_yr_erosion))

x2 <- x1 %>%
  mutate(Percent = round(100*(total_impaired/total_str_num),2))

x3 <- x2 %>%
  select(-total_str_num, -total_impaired) %>%
  pivot_wider(names_from = Year, values_from = Percent)
x3 <- x3 %>%
  mutate(Notes = "ratings >= 3")
```

```{r, echo = FALSE}

kable(x3, caption = "Erosion Diagnoses of 3 or 4 or 5", digits = 3)

```
Rootwad: Denominator is total number number of rootwad structures (22)
```{r, include = FALSE}
x <- RA
rtwads <- x %>%
  filter(!is.na(Rootwad_Performance))
rtwads_structures <- length(unique(rtwads$Num))

x <- find_first_year_of_impairment_Rootwad(rtwads)


x1 <- x %>%
  group_by(Year, Structure_Type) %>%
  summarise(total_str_num = length(unique(Num)),
            total_impaired = sum(fir_imp_yr_rootwad))

x2 <- x1 %>%
  mutate(Percent = round(100*(total_impaired/total_str_num),2))

x3 <- x2 %>%
  select(-total_str_num, -total_impaired) %>%
  pivot_wider(names_from = Year, values_from = Percent)
x3 <- x3 %>%
  mutate(Notes = "ratings >= 3")
```

```{r, echo = FALSE}

kable(x3, caption = "Rootwad Diagnoses of 3 or 4 or 5", digits = 3)

```
## Max Scores
Integrity
```{r, include = FALSE}
x <- RA
x1 <- x %>%
  filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
  select(Num, Structure_Type, Year, Integrity)
###INTEGRITY
###total summarized for all structures
total <- x1 %>%
  group_by(Structure_Type, Num) %>%
  summarize(max_int = max(Integrity))

total2 <- total %>%
  ungroup() %>%
  count(max_int) %>%
  rename(Integrity = max_int,
         Max = n) 

#year by year
x2 <- x1 %>%
  pivot_wider(names_from = Year, values_from = Integrity) %>%
  rowwise() %>%
  mutate(max_int = max(c(`2014`,`2015`,`2016`,`2017`,`2018`,`2020`)))


x2 <- x %>%
  filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
  count(Integrity, Year) %>%
  pivot_wider(names_from = Year, values_from = n)

# x3 <- x %>%
#   filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
#   count(Integrity) 

all_structures_max_summarized <- left_join(x2, total2, by = "Integrity")
all_structures_max_summarized[is.na(all_structures_max_summarized)] <- 0
```

```{r, echo = FALSE}
kable(all_structures_max_summarized, caption = "Integrity Scores by Year")
```
Deposition
```{r, include = FALSE}

###DEPOSITOIN

x <- RA
x1 <- x %>%
  filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
  select(Num, Structure_Type, Year, Deposition)
###total summarized for all structures
total <- x1 %>%
  group_by(Structure_Type, Num) %>%
  summarize(max_dep = max(Deposition))

total2 <- total %>%
  ungroup() %>%
  count(max_dep) %>%
  rename(Deposition = max_dep,
         Max = n) 

#year by year
# x2 <- x1 %>%
#   pivot_wider(names_from = Year, values_from = Deposition) %>%
#   rowwise() %>%
#   mutate(max_int = max(c(`2014`,`2015`,`2016`,`2017`,`2018`,`2020`)))


x2 <- x %>%
  filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
  count(Deposition, Year) %>%
  pivot_wider(names_from = Year, values_from = n)

# x3 <- x %>%
#   filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
#   count(Integrity) 

all_structures_max_summarized <- left_join(x2, total2, by = "Deposition")
all_structures_max_summarized[is.na(all_structures_max_summarized)] <- 0
```

```{r, echo = FALSE}
kable(all_structures_max_summarized, caption = "Deposition Scores by Year")

```
Erosion
```{r, include = FALSE}

###Erosion

x <- RA
x1 <- x %>%
  filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
  select(Num, Structure_Type, Year, Erosion)
###total summarized for all structures
total <- x1 %>%
  group_by(Structure_Type, Num) %>%
  summarize(max_ero = max(Erosion))

total2 <- total %>%
  ungroup() %>%
  count(max_ero) %>%
  rename(Erosion = max_ero,
         Max = n) 

#year by year
# x2 <- x1 %>%
#   pivot_wider(names_from = Year, values_from = Erosion) %>%
#   rowwise() %>%
#   mutate(max_int = max(c(`2014`,`2015`,`2016`,`2017`,`2018`,`2020`)))


x2 <- x %>%
  filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
  count(Erosion, Year) %>%
  pivot_wider(names_from = Year, values_from = n)

# x3 <- x %>%
#   filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
#   count(Integrity) 

all_structures_max_summarized <- left_join(x2, total2, by = "Erosion")
all_structures_max_summarized[is.na(all_structures_max_summarized)] <- 0
```

```{r, echo = FALSE}
kable(all_structures_max_summarized, caption = "Erosion Scores by Year")

```
Rootwad
```{r, include = FALSE}

###Rootwad

x <- RA
x1 <- x %>%
  filter(!is.na(Rootwad_Performance)) %>%
  select(Num, Structure_Type, Year, Rootwad_Performance)
###total summarized for all structures
total <- x1 %>%
  group_by(Structure_Type, Num) %>%
  summarize(max_roo = max(Rootwad_Performance))

total2 <- total %>%
  ungroup() %>%
  count(max_roo) %>%
  rename(Rootwad_Performance = max_roo,
         Max = n) 

#year by year
# x2 <- x1 %>%
#   pivot_wider(names_from = Year, values_from = Rootwad_Performance) %>%
#   rowwise() %>%
#   mutate(max_int = max(c(`2014`,`2015`,`2016`,`2017`,`2018`,`2020`)))


x2 <- x %>%
  filter(!is.na(Rootwad_Performance)) %>%
  count(Rootwad_Performance, Year) %>%
  pivot_wider(names_from = Year, values_from = n)

# x3 <- x %>%
#   filter(!is.na(Integrity) | !is.na(Deposition) | !is.na(Erosion)) %>%
#   count(Integrity) 

all_structures_max_summarized <- left_join(x2, total2, by = "Rootwad_Performance")
all_structures_max_summarized[is.na(all_structures_max_summarized)] <- 0


```

```{r, echo = FALSE}
kable(all_structures_max_summarized, caption = "Rootwad Scores by Year")

```


## RA max Scores Given to a structure Type 
```{r, echo = FALSE}
x <- RA
max_structure_scores <- x %>%
  filter(!is.na(Integrity)) %>%
  group_by(Structure_Type, Year) %>%
  summarise(max_int_score = max(Integrity))

max_structure_scores %>%
  ggplot(aes(x = Year, y = max_int_score, fill = Structure_Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  labs(title = "Max Integrity Scores for Structures Across Years", x = "Year", y = "Max Integrity Score")

```

## RA Integrity for all Structures

Showing the state of structures. These don't show new diagnoses, so a structure that could have been a 3 in past years may still be a 3 in subsequent years. 
```{r,include =FALSE}
###Integrity andfucntion of all structures
x <- RA
# x1 <- x %>%
#   group_by(Integrity, Year) %>%
#   summarise(total = sum())

x1 <- x %>%
  filter(!is.na(Integrity)) %>%
  count(Integrity, Year) %>%
  mutate(Percent = round(100*(n / length(unique(RA$Num))),2))
x2 <- x1 %>%
  select(-n) %>%
  pivot_wider(names_from = Year,values_from = Percent)

x2[is.na(x2)] <- 0

```
Denominator is total structures (137)
```{r, echo = FALSE}
kable(x2, caption = "Integrity of all Habitat Structures")
```
Deposition 
```{r, include = FALSE}
x1 <- x %>%
  filter(!is.na(Deposition)) %>%
  count(Deposition, Year) %>%
  mutate(Percent = round(100*(n / length(unique(RA$Num))),2))
x2 <- x1 %>%
  select(-n) %>%
  pivot_wider(names_from = Year,values_from = Percent)

x2[is.na(x2)] <- 0
```

```{r, echo = FALSE}
kable(x2, caption = "Deposition of all Habitat Structures")
```
Erosion
```{r, include=FALSE}
x1 <- x %>%
  filter(!is.na(Erosion)) %>%
  count(Erosion, Year) %>%
  mutate(Percent = round(100*(n / length(unique(RA$Num))),2))
x2 <- x1 %>%
  select(-n) %>%
  pivot_wider(names_from = Year,values_from = Percent)

x2[is.na(x2)] <- 0
```

```{r, echo = FALSE}
kable(x2, caption = "Erosion of all Habitat Structures")
```

Rootwads: Denominator is all Rootwad structures
```{r, include = FALSE}
x1 <- x %>%
  filter(!is.na(Rootwad_Performance)) %>%
  count(Rootwad_Performance, Year) %>%
  mutate(Percent = round(100*(n / rtwads_structures),2))
x2 <- x1 %>%
  select(-n) %>%
  pivot_wider(names_from = Year,values_from = Percent)

x2[is.na(x2)] <- 0
```

```{r, echo = FALSE}
kable(x2, caption = "Rootwad Scores of all Rootwad Structures")
```
